The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History Could Be Far More Interesting\altaffilmark{1}

### 2012-12-29 2012-aqs/draft-aqs.tex
Updated velocities + some text

C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & \dots & $-$169.0	& \dots & 0.7 \\
C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & \dots & $-$239.3	& \dots & 0.6 \\
HD41667			& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
HD142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
J221821-183424	& 22:18:21.2	& $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & \dots & $-$170.5	& \dots & 0.5 \\
J223504-152834	& 22:35:04.5	& $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & \dots & $-$180.9	& \dots & 0.7 \\
J223811-104126	& 22:38:11.6	& $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & \dots & $-$248.4	& \dots & 0.7

@@

With our spectrum at near-rest, we measured the equivalent widths of $\sim$200 lines by fitting Gaussian functions to the absorption profiles. Fitted Gaussian profiles provides us with a measured equivalent width, the full-width half-maximum of the profile, and the central wavelength. Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths. The final radial velocity for the star is provided by the mean of these $\sim$200 line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree excellently (within X\,km s$^{-1}$) with previously reported literature values \citep{williams;et-al_2011,wylie-de-boer;et-al_2012}, demonstrating the accuracy of the radial velocities published by the RAVE survey.

@@

Surface gravity was found by forcing the mean Fe\,I and Fe\,II abundances to be equal, whilst maintaining zero trends with the excitation potential, reduced equivalent width and abundance. After these parameters had converged, the model metallicity was exactly matched to that of our line abundances. Line abundances that were unusually deviant ($3\sigma$) from the mean were removed. The largest number of outlier measurements removed for any observation was N for X.

@@

% calcium measurements + silicon measurements
Of all the $\alpha$-elements, calcium has the smallest measurement scatter in our stars. Four line measurements were used for each star, with a measurement uncertainty of 0.01\,dex. As shown in Figure \ref{fig:alpha-elements}, all Aquarius stars show super-solar Ca abundances, ranging between 0.23 to 0.43 dex, consistent with both [Mg/Fe] and [Si/Fe] measurements. However, C2225316-14437 has an unusually high silicon abundance ($\mbox{[Si/Fe]} = 0.72$), well outside the uncertainties of the rest of our sample. C2225316-14437 does not demonstrate unusually high abundances of any other $\alpha$-element, and the silicon lines are not affected by telluric absorption. Moreover, the Si lines are in relatively good agreement with one another. If we exclude the most prominent outlier, then the mean abundance drops only slightly to $\mbox{[Si/Fe]} = 0.70 \pm 0.04$\,dex. The lowest silicon line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, still significantly higher than the final measurements for any other star.

@@

\subsubsection{Iron-peak Elements}
Scantium, Vanadium, Chromium and Manganese. All very vanilla, exhibiting a downward trend with [Fe/H].
Data.

@@

Our standard stars have [Ba/Fe] abundances very typical of the Milky Way halo. Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra. We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is in rough accordance with existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.

@@

% [Na/Fe], [Ni/Fe]
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/aquarius-na-ni.pdf}
	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars.}
	\label{fig:na-ni}
\end{figure}

@@

Since the Aquarius stream is kinematically coherent, the default assumption is that the system has been accreted.
% their chemistry is indicative of not belonging to a dwarf spheroidal

>>>>

C2225316-14437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033 & \dots & \dots & 135	 & --168.6	& --156.4 & 0.1 \\
C2306265-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096 & \dots & \dots & 100	 & --240.4	& --221.1 & 0.1 \\
HD41667			& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
HD142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\
J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& \dots & \dots & 115 	 & --170.2	& --159.5 & 0.1 \\
J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& \dots & \dots & 135	 & --179.0	& --169.7 & 0.1 \\
J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& \dots & \dots & 115	 & --250.1	& --235.7 & 0.1

% V corrections (already applied the first number of each row)
% J221821     	:   0.30, 0.25 +/- 1.25 (MEK has -154.1, wdb ) -- diff: 5.4  (positive == higher)
% C2225316		:	0.43, 0.42 +/- 1.13 (MEK has -155.7) -- diff: -0.4 (hers is lower)
% C2306265		: 	1.14, 1.19 +/- 1.16 (MEK has -221.8) -- diff: -0.7 (hers is lower)
% J223504		:	-1.87, -1.89 +/- 1.45 (MEK has -166.9) -- diff: 2.8 (positive == higher)
% J223811		:	1.69, 1.61	+/- 1.47 (MEK has --230.1) -- diff 5.6 (positive == higher)

@@

With our spectrum at near-rest, we measured the equivalent widths of $\sim$200 lines by fitting Gaussian functions to the absorption profiles. Fitted Gaussian profiles provides us with a measured equivalent width, the full-width half-maximum of the profile, and the central wavelength. Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths. The final radial velocity for the star is provided by the mean of these $\sim$200 line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: $\langle\Delta{V_{hel}}\rangle = 2.8$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published by the RAVE survey.

@@

Surface gravity was found by forcing the mean Fe\,I and Fe\,II abundances to be equal, whilst maintaining zero trends with the excitation potential, reduced equivalent width and abundance. After these parameters had converged, the model metallicity was exactly matched to that of our line abundances. Line abundances that were unusually deviant ($3\sigma$) from the mean were removed. The largest number of outlier measurements removed for any observation was nine for C222531-144370.

@@

% calcium measurements + silicon measurements
Of all the $\alpha$-elements, calcium has the smallest measurement scatter in our stars. Four line measurements were used for each star, with a measurement uncertainty of 0.01\,dex. As shown in Figure \ref{fig:alpha-elements}, all Aquarius stars show super-solar Ca abundances, ranging between 0.23 to 0.43 dex, consistent with both [Mg/Fe] and [Si/Fe] measurements. However, C2225316-14437 has an unusually high silicon abundance ($\mbox{[Si/Fe]} = 0.72$), well outside the uncertainties of the rest of our sample. C2225316-14437 does not demonstrate unusually high abundances of any other $\alpha$-element, and the silicon lines are not affected by telluric absorption. Moreover, the Si lines are in relatively good agreement with one another. If we exclude the most prominent outlier, then the mean abundance drops only slightly to $\mbox{[Si/Fe]} = 0.70 \pm 0.04$\,dex. The lowest silicon line abundance for C2225316-14437 is $\mbox{[Si/Fe]} = 0.57$\,dex, still significantly higher than the averaged abundance for any other star.

@@

\subsubsection{Aluminium}
There are six aluminium transition lines available in our optical spectra. The strongest of these lines occur at 3944 and 3961\,{\AA}, and are visible in all of our stars. However, this is a particularly crowded spectral region: these lines fall between the strong Ca H and K lines, with the 3961\,{\AA} transition clearly in the wing of the Ca H line. This makes the continuum determination and subsequent Al measurement non-trivial, especially given the metallicity of our stars. Instead, we have measured Al abundances from the other transitions available in our spectra: the Al \textsc{I} lines at 6696, 6698, 7835 and 7836\,{\AA}. Although these lines are weaker than the bluer Al \textsc{I} lines, their surrounding regions are uncrowded.

Generally the four Al \textsc{i} lines are in reasonable agreement with one another, yielding random scatter of less than 0.05\,dex.

These lines were not always detected in our spectra. With decreasing metallicity and increasing temperature the strength of the lines is noticeably weakened, below a 3-$\sigma$ detection limit. For our most metal-poor star, J221821, only one Al \textsc{i} line was detectable, and we have adopted an uncertainty of 0.05\,dex.

% there are a few lines available in the spectrum
% incl. blue ones
% the blue ones remain strong even in extremely metal-poor stars
% in metal rich stars the region is too crowded and the continuum (and abundance) is non-trivial to determine
% in lieu of using these lines, we have used 4 other lines at X
% for our most metal-poor star, J221X, only one of these lines was detectable

\subsubsection{Iron-peak Elements (Sc, V, Cr and Mn)}
Scantium, Vanadium, Chromium and Manganese. All very vanilla, exhibiting a downward trend with [Fe/H].
Data.

@@

Our standard stars have [Ba/Fe] abundances very typical of the Milky Way halo. Only one of our standard stars, HD 44007, has published [Ba/Fe] abundances from high-resolution spectra. We find HD 44007 to have $\mbox{[Ba/Fe]} = -0.05 \pm 0.04$, which is in between existing published measurements from \citet{fulbright_2000} and \citet{burris;et-al_2000} of $-0.27$ and 0.05 dex, respectively.

@@

% [Na/Fe], [Ni/Fe]
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/aquarius-na-ni.pdf}
	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars. TODO add dwarf/GC/disk stars on here.}
	\label{fig:na-ni}
\end{figure}

@@

Since the Aquarius stream is kinematically coherent, the default assumption is that the system has been accreted.

% their chemistry is indicative of not belonging to a dwarf spheroidal
